\Title

### 2020-02-05 manuscript/manuscript.tex
Redefine symbols for scaled matrix and coefs vector

\begin{equation}
    V(\mathbf{p})
    =
    \mathbf{A} \mathbf{S}^{-1} \mathbf{S} \mathbf{c}
    =
    \left[
        \mathbf{A} \mathbf{S}^{-1}
    \right]
    \left[
        \mathbf{S} \mathbf{c}
    \right]
    =
    \mathbf{A}' \mathbf{c}'
\end{equation}

\noindent where $\mathbf{A}'$ the scaled Jacobian matrix and $\mathbf{c}'$ is
a vector containing scaled coefficients.

@@

\begin{equation}
    \phi(\mathbf{c'}) =
        \left\lVert V(\mathbf{p}) - \mathbf{A}'\mathbf{c}' \right\rVert ^ 2
        + \lambda \left\lVert \mathbf{c}' \right\rVert ^2,
    \label{eq:misfit}
\end{equation}

@@

After solving the least squares problem, we obtain the set of scaled
coefficients $\mathbf{c}'$ that minimizes equation~\ref{eq:misfit}.
We can get the corresponding coefficients $\mathbf{c}$ by rescaling
$\mathbf{c}'$:

\begin{equation}
    \mathbf{c} = \mathbf{S}^{-1} \mathbf{c}'.
\end{equation}

>>>>

\begin{equation}
    V(\mathbf{p})
    =
    \mathbf{A} \mathbf{S}^{-1} \mathbf{S} \mathbf{c}
    =
    \left[
        \mathbf{A} \mathbf{S}^{-1}
    \right]
    \left[
        \mathbf{S} \mathbf{c}
    \right]
    =
    \mathbf{A_s} \mathbf{c_s}
\end{equation}

\noindent where $\mathbf{A_s}$ the scaled Jacobian matrix and $\mathbf{c_s}$ is
a vector containing scaled coefficients.

@@

\begin{equation}
    \phi(\mathbf{c'}) =
        \left\lVert V(\mathbf{p}) - \mathbf{A_s}\mathbf{c_s} \right\rVert ^ 2
        + \lambda \left\lVert \mathbf{c_s} \right\rVert ^2,
    \label{eq:misfit}
\end{equation}

@@

After solving the least squares problem, we obtain the set of scaled
coefficients $\mathbf{c_s}$ that minimizes equation~\ref{eq:misfit}.
We can get the corresponding coefficients $\mathbf{c}$ by rescaling
$\mathbf{c_s}$:

\begin{equation}
    \mathbf{c} = \mathbf{S}^{-1} \mathbf{c_s}.
\end{equation}
